---
title: "Exploring the use of Shiny in R Markdown"
author: "Shinygroup"
date: '2022'
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
require("rstudioapi")
knitr::opts_chunk$set(echo = TRUE)

# Locating the file and setting up the work directory
location <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(location)

# Loading the required packages and data 
source(paste(location,"preload.R", sep = "/"))
source(paste(location,"data_prepration.R", sep = "/"))
```

The goal of this R Markdown document is to explore the use of Shiny for making interactive documents. Two topics are discussed in this document. The first chapter is dedicated to visualize how railway bridge components deteriorate overtime. This will provide asset managers with an overview of the how their assets behave overtime and what maintenance actives are needed. The second chapter visualizes the emission of CO2. The markdown will provide a countrywise emissions data and then provide a projected amount to be removed from the atmosphere by the year 2050. Also, it can show the user the percentage contribution of their carbon removal efforts in the total carbon dioxide curbs required by the year 2050.

Multiple packages are used to maximize the interactivity of this document and bring the result of analysis at the tips of user fingers.

## Chapter 1: Visualising the deterioration of railway bridges

This document considers an illustrative example railway network located in the canton of Bern, Switzerland. Different visualizations are created to assist infrastructure mangers in their intervention planning process. The figure below shows the approximate location of the canton of Bern.

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# map_data_ch <- map_data('world')[map_data('world')$region == "Switzerland",]
# swiss_map <- ggplot() +
  ## First layer: worldwide map
#  geom_polygon(data = map_data("world"),
#               aes(x=long, y=lat, group = group),
#               color = '#9c9c9c', fill = '#f3f3f3') +
  ## Second layer: Country map
#  geom_polygon(data = map_data_ch,
#               aes(x=long, y=lat, group = group),
#               color = 'red', fill="#b01040") +
#  coord_map() +
#  coord_fixed(1.3,
#              xlim = c(5.970019, 10.454590),
#              ylim = c(45.83003, 47.77563)) +
#  ggtitle("A map of Switzerland") +
#  theme(panel.background =element_rect(fill = 'blue'))+
#  theme(axis.title = element_blank())+
#  theme(axis.ticks = element_blank())+
#  theme(axis.text = element_blank())

#swiss_map
```

```{r echo=FALSE}


json_ch <- jsonlite::read_json(
  "https://raw.githubusercontent.com/mbannert/maps/master/ch_bfs_regions.geojson"
)

d <- data.frame(
  name = c("Zürich",
           "Ticino",
           "Zentralschweiz",
           "Nordwestschweiz",
           "Espace Mittelland",
           "Région lémanique",
           "Ostschweiz"),
  values = c(20,20,20,20,100,20,20)
)

d |>
  e_charts(name) |>
  e_map_register("CH", json_ch) |>
  e_map(serie = values, map = "CH") |>
  e_visual_map(values,
               inRange = list(color = viridis(7)))

```

In Switzerland asset managers use a scale of 1-5 to keep track of the condition of their asset.

| Condition state | Condition description | Damage description   |
|-----------------|-----------------------|----------------------|
| 1               | Good                  | None                 |
| 2               | Acceptable            | Minor                |
| 3               | Damaged               | Significant          |
| 4               | Poor                  | Extensive            |
| 5               | Alarmin               | Safety is endangered |

: Definition of the condition states

```{r}

```

The first insight an asset manager wants to have is knowing the current condition of the assets. Having such information also provides a basis for the predicting the evolution of the condition states over time. By having an interactive document, asset managers can easily get the latest overview of the condition of their assets. For example, the latest overall condition of the bridges in the mentioned line can be observed per each bridge category using the dynamic bar chart below.

```{r select-input, echo=FALSE}
   selectInput(
  inputId = 'bridge_type',
  label = 'Please specify the type of the bridges',
  choices = list('Steel'=1,
                 'Concrete'=2,
                 'Masonry'=3,
                 'Composite'=4,
                 'ALL'=5)
)

```

```{r render-plot}

  output$p1 <- renderPlotly({
    if (input$bridge_type == 1) {
      cat("Steel")
    }
    
    
  }
    
    
  )
  
```

The evolution of the condition states overtime can be easily seen by moving the slide.

```{r slider-input}
  sliderInput(inputId = "date_year", label = "Selected year:",
              min = year(today()), max = year(today())+14, value = year(today()), step = 1)
```

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change. This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.

## Chapter 2: Worldwide CO2 Emissions

World Map to show various countries and their emissions in the year 2016.

```{r}

data <- read.csv(paste(location,"Data/emissions.csv", sep = "/"))

#Filling any left coordinates
data <- data[complete.cases(data),]

#ensuring lat and long are numbers
data$longitude <- as.numeric(data$longitude)
data$latitude <- as.numeric(data$latitude)

#creating new spatial point dataframe
data.SP <- SpatialPointsDataFrame(data[,c(7,8)], data[,-c(7,8)])
  
m <- leaflet() %>% 
  addTiles() %>% 
  addMarkers(data = data, lng= ~longitude, lat= ~latitude, popup= paste(data$Country, "<br>", data$Emissions) )

m
```
