---
title: "Exploring the use of Shiny in R Markdown"
author: "Shinygroup"
date: '2022'
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
require("rstudioapi")
knitr::opts_chunk$set(echo = TRUE)

# Locating the file and setting up the work directory
location <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(location)

# Loading the required packages and data 
source(paste(location,"preload.R", sep = "/"))
source(paste(location,"data_prepration.R", sep = "/"))
```

The goal of this R Markdown document is to explore the use of Shiny for making interactive documents. Two topics are discussed in this document. The first chapter is dedicated to visualize how railway bridge components deteriorate overtime. This will provide asset managers with an overview of the how their assets behave overtime and what maintenance actives are needed. The second chapter visualizes the emission of CO2. The markdown will provide a countrywise emissions data and then provide a projected amount to be removed from the atmosphere by the year 2050. Also, it can show the user the percentage contribution of their carbon removal efforts in the total carbon dioxide curbs required by the year 2050.

Multiple packages are used to maximize the interactivity of this document and bring the result of analysis at the tips of user fingers.

## Chapter 1: Visualising the deterioration of railway bridges

This document considers an illustrative example railway network located in the canton of Bern, Switzerland. Different visualizations are created to assist infrastructure mangers in their intervention planning process. The figure below shows the approximate location of the canton of Bern.

<<<<<<< HEAD
In a first step, we will try to visualize the locations of the bridges in Switzerland. For this, we first read in the data pertaining to the bridges themselves, and then the data linking these bridges with their longitude and latitude. 

```
install.packages("readxl")
library(readxl)

bridges_coordinates <- read_excel("bridges_coordinates.xlsx")
ZolBgg <- read_excel("ZolBgg-xmp.xlsx")

names <- na.omit(ZolBgg[,2]) # we create a vector with the bridge names that we can add the coordinates too 
# we use this vector to then match the coordinates with the bridges, in order to visualize them on a map 

bridges_coordinates$Name
names.bridges <- c("Aarebr. Bruegg", "Aareviad Busswil", "Du Chueelibach", "Du Lyssbach", "Jenskanal-Br.", "KDu Loeribach", 
                   "PDu Horbengasse", "Plle Bruegg", "PU Schuepfen", "PU Bruegg mitte 3", "PU Busswil", "PU Lyss", "PU mitte 1", 
                   "PU Muenchenbuchsee", "PU Oberfeldweg", "PU Studen Station", "PU Suberg", "SU Brueggstrasse Sued", "SU Fluehmatten", 
                   "SU Leueren Blaumatt", "SU Muehleplatz", "SU Murgeli", "SU Rosengasse", "SU Schwanden", "SU Studen", "SUe Bruegg",
                   "SUe Steinweg", "U Bielstr.", "U Bielstrase", "U Neubrueckstrasse", "Ue Brueggstrasse", "WU Friedhof", "WU Holen")

# we now rename the brige coordinates that we have
# we will then use this to match the coordinates with the bridge names (for which we have deteoriation data)

bridges_coordinates$Name <- c("Aarebr. Bruegg", "Aareviad Busswil", "Du Lyssbach", "Du Chueelibach", "Jenskanal-Br.", "KDu Loeribach", 
                              "PDu Horbengasse", "Plle Bruegg", "PU Bruegg mitte 3", "no data", "no data", "no data", "no data", "no data", 
                              "PU Busswil", "PU Lyss", "PU mitte 1", "no data", "no data", "no data", "no data", "no data", "PU Muenchenbuchsee", 
                              "PU Oberfeldweg", "no data", "PU Studen Station", "PU Suberg", "SU Brueggstrasse Sued", "SU Fluehmatte", 
                              "SU Leueren Blaumatt", "SU Muehleplatz", "SU Murgeli", "SU Rosengasse", "SU Schwanden", "SU Studen", "SUe Bruegg", 
                              "SUe Steinweg", "U Bielstr.", "U Bielstrasse", "U Neubrueckstrasse", "no data", "Ue Brueggstrasse", "WU Friedhof", "WU Holen")

names.bridges <- as.data.frame(names.bridges)
names.bridges$Name <- names.bridges$names.bridges

bridges <- merge(names.bridges, bridges_coordinates, by = "Name", all.y = TRUE)
View(bridges) 
bridges <- subset(bridges, bridges$Name != "no data") # we now have a dataset containing only the observations for which we have data available regarding their deterioration
bridges.noNA <- na.omit(bridges)


# plotting the data on a map of Switzerland 
map_data_ch <- map_data('world')[map_data('world')$region == "Switzerland",]
swiss_map <- ggplot() + geom_polygon(data = map_data_ch,
                                                    aes(x=long, y=lat, group = group),
                                                   color = 'red', fill="#b01040")
```

```{r echo=FALSE}
#=======
#```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
#>>>>>>> d820fb64afddd2de172013429059a5bb3884cd70

# map_data_ch <- map_data('world')[map_data('world')$region == "Switzerland",]
# swiss_map <- ggplot() +
  ## First layer: worldwide map
#  geom_polygon(data = map_data("world"),
#               aes(x=long, y=lat, group = group),
#               color = '#9c9c9c', fill = '#f3f3f3') +
  ## Second layer: Country map
#  geom_polygon(data = map_data_ch,
#               aes(x=long, y=lat, group = group),
#               color = 'red', fill="#b01040") +
#  coord_map() +
#  coord_fixed(1.3,
#              xlim = c(5.970019, 10.454590),
#              ylim = c(45.83003, 47.77563)) +
#  ggtitle("A map of Switzerland") +
#  theme(panel.background =element_rect(fill = 'blue'))+
#  theme(axis.title = element_blank())+
#  theme(axis.ticks = element_blank())+
#  theme(axis.text = element_blank())

#swiss_map
```

```{r echo=FALSE}


json_ch <- jsonlite::read_json(
  "https://raw.githubusercontent.com/mbannert/maps/master/ch_bfs_regions.geojson"
)

d <- data.frame(
  name = c("Zürich",
           "Ticino",
           "Zentralschweiz",
           "Nordwestschweiz",
           "Espace Mittelland",
           "Région lémanique",
           "Ostschweiz"),
  values = c(20,20,20,20,100,20,20)
)

d |>
  e_charts(name) |>
  e_map_register("CH", json_ch) |>
  e_map(serie = values, map = "CH") |>
  e_visual_map(values,
               inRange = list(color = viridis(7)))

```

In Switzerland asset managers use a scale of 1-5 to keep track of the condition of their asset. An example of the condition state definition are shown in the table below:

| Condition state | Condition description | Damage description   |
|-----------------|-----------------------|----------------------|
| 1               | Good                  | None                 |
| 2               | Acceptable            | Minor                |
| 3               | Damaged               | Significant          |
| 4               | Poor                  | Extensive            |
| 5               | Alarmin               | Safety is endangered |

: Definition of the condition states

The first insight an asset manager wants to have is knowing the current condition of the assets. Such information also provides a basis for the predicting the evolution of the condition states over time. By having an interactive document, asset managers can easily get the latest overview of the condition of their assets. For example, the latest overall condition of the bridges in the mentioned line can be observed per each bridge category using the dynamic bar chart below.

```{r select-input, echo=FALSE}

# Getting the input
   selectInput(
  inputId = 'bridge_type',
  label = 'Please specify the type of the bridges',
  choices = list('ALL',
                 'Concrete',
                 'Masonry',
                 'Composite',
                 'Steel')
)

# Producing the right graph according to the input!
renderPlotly( {
bridge_typ <- input$bridge_type

if (input$bridge_type == "ALL") {
  
  bar_data_2 <- components %>% count(Type, CS) %>% group_by(Type) %>% mutate(probability = (n/sum(n)*100))
  bar_plot_2<- plot_ly(bar_data_2, x = ~Type, y = ~probability , color = ~CS ,type = "bar",
                     text = ~probability %>% round() ) %>% layout(yaxis = list(ticksuffix = "%") ) 
  
} else {
  
  bar_data_2 <- components %>% filter(Type == bridge_typ) %>% count(Type, CS) %>% group_by(Type) %>% 
    mutate(probability = (n/sum(n)*100))
  bar_plot_2<- plot_ly(bar_data_2, x = ~Type, y = ~probability , color = ~CS ,type = "bar",
                     text = ~probability %>% round() ) %>% layout(yaxis = list(ticksuffix = "%") ) 
}
} )
```
The evolution of the condition states overtime are predicted using Markov chain modelling. 





The evolution of the condition states overtime can be easily seen by moving the slide.

```{r slider-input, echo=TRUE}


  sliderInput(inputId = "date_year", label = "Selected year:",
              min = year(today()), max = year(today())+14, value = year(today()), step = 1,
              animate = animationOptions(interval = 500, loop = TRUE))


```

```{r}
shinyAppDir(
  location,
  options = list(
    width = "100%", height = 550
  )
)
```

## Chapter 2: Worldwide CO2 Emissions

World Map to show various countries and their emissions in the year 2016.

```{r}

data <- read.csv(paste(location,"Data/emissions.csv", sep = "/"))

#Filling any left coordinates
data <- data[complete.cases(data),]

#ensuring lat and long are numbers
data$longitude <- as.numeric(data$longitude)
data$latitude <- as.numeric(data$latitude)

#creating new spatial point dataframe
data.SP <- SpatialPointsDataFrame(data[,c(7,8)], data[,-c(7,8)])
  
m <- leaflet() %>% 
  addTiles() %>% 
  addMarkers(data = data, lng= ~longitude, lat= ~latitude, popup= paste(data$Country, "<br>", data$Emissions) )

m
```

```{r}
ui <- fluidPage(

    # Application title
    titlePanel("CO2 Emissions Projection by 2050"),

    # Sidebar with a slider input for number of bins 
    sidebarLayout(
        sidebarPanel(
            sliderInput("R",
                        "Kgs per month",
                        min = 0,
                        max = 10,
                        value = 1),
            sliderInput("f",
                        "yo",
                        min = 0,
                        max = 10,
                        value = 1)
        ),

        # Show a plot of the generated distribution
        mainPanel(
           plotOutput("distPlot")
        )
    )
)

# Define server logic required to draw the plot
server <- function(input, output) {

    output$distPlot <- renderPlot({
        # generate bins based on input$bins from ui.R
        s    <- 1:100
        V = input$R*exp(-1*input$f*s)

        # draw the plot with the specified number of bins
        plot(s,V, col = 'darkgray',
             xlab = 'Waiting time to next eruption (in mins)',
             main = 'Plot of waiting times', bty="n",type="l")
    })
}

# Run the application 
shinyApp(ui = ui, server = server)
```

=======

